Frame Competition

### 2022-07-06 paper/Manuscript.Rmd
Update vector plot and descriptions

Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*. This way, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing. This could well be done with document embeddings as well, however topic vectors offer a key advantage here: other than the dimensions of a, say, 300-dimensional embedding model, the dimensions of topic-vectors are interpretable. This can serve as a sanity check (e.g. if increased attention to crime results in higher similarity to a left-wing party that supports extended immigration, this would suggest that the model is not great), as well as enrich the data analysis: if frame similarity has an effect on parties' electoral prospects, it is easy to see which topics drive this effect and how the media debate affected opinion polls.

>>>>

Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*. Figure \@ref(fig:vectors) gives a two-dimensional example: the article vector (representing the distribution of different considerations within the article) is clearly closer to the vector of party a (representing the distribution of considerations in party a's communication), compared to party b.

With this approach, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing. This could well be done with document embeddings as well, however topic vectors offer a key advantage here: other than the dimensions of a, say, 300-dimensional embedding model, the dimensions of topic-vectors are interpretable. This can serve as a sanity check (e.g. if increased attention to crime results in higher similarity to a left-wing party that supports extended immigration, this would suggest that the model is not great), as well as enrich the data analysis: if frame similarity has an effect on parties' electoral prospects, it is easy to see which topics drive this effect and how the media debate affected opinion polls.

```{r vectors}

data.frame(
  item = c("article", "Party A", "Party B",
            "article", "Party A", "Party B"),
  dim1 = c(0,  0.2, 0.8,
            0,0,0),
  dim2 = c(1, 0.8, 0.2,
            0,0,0)
) %>% 
ggplot(aes(x = dim1, y = dim2, 
        color = item, linetype = item)) +
  geom_line() +
  geom_point(alpha = 0.3) + 
  theme_minimal() +
  xlab("Attention to Consideration 1") +
  ylab("Attention to Consideration 2") +
  theme(legend.title = element_blank())
